### 2011-09-09 paper.tex
length distributions

@@

>>>>

The {\em inside sequence} refers to the sequences $\outsubseq{i}{j}$ and $\outsubseq{k}{l}$ (for $\m$),
or the sequence $\outsubseq{i}{l}$ (for $\mtip$).

@@

\subsubsection{Length distributions}

To model genomic features, it is extremely useful to augment the TAG framework with length distributions;
that is, to allow the rule weight $\weight(\rho)$ to depend on the distances $j-i$, $k-j$, $l-k$ and on the sum of these, $l-i$.

Note that the TAG framework implicitly allows some length distributions to be constructed;
for example, the ``waiting time'' of a particular node label
(e.g. the number of type-6 rules with $B=A$ that are applied before a rule with $B \neq A$ is eventually applied,
so that the intermediate tree effectively ``leaves'' state $A$) is geometrically-distributed, and by arranging a series of such states,
one can obtain other distributions, e.g. a negative binomial distribution.
One can also obtain any distribution over a random variable $x \leq N$ by using $N$ states.
However, it is often much more convenient and efficient simply to allow $\weight$ to sometimes depend directly on the inside sequence length.
